---
title: "Comparison of Control and Treatment Groups"
author:
  - name: "Your Name"
    affiliation: "Department of Entomology, Example University, City, Country"
date: today
keywords:
  - insect physiology
  - treatment effects
  - statistical analysis
abstract: |
  This study compares measurements between control and treatment groups across
  two measurement dates. We performed t-tests and linear regression analysis to
  evaluate differences. Treatment group exhibited significantly elevated values
  compared to control group.
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(ggplot2)

# Load pre-computed analysis results
results <- readRDS("output/analysis_results.rds")
```

## Introduction

Understanding differences between experimental conditions is fundamental to scientific research.
This analysis compares measurements collected from control and treatment groups to evaluate whether
the experimental intervention produces measurable changes. We hypothesized that the treatment would
result in elevated measurements compared to controls.

## Methods

### Study Design and Data

We collected measurements from both control and treatment groups on two separate dates
(January 15 and January 20, 2024). A total of 20 observations were recorded (10 per group,
with measurements repeated across two dates). One measurement in the control group was excluded
due to missing data.

### Statistical Analysis

We employed two complementary approaches to evaluate group differences:

1. **T-test**: A two-sample t-test compared mean values between groups, with statistical
   significance assessed at α = 0.05.

2. **Linear regression**: A simple linear model with group as the predictor was fit to the data
   to quantify the magnitude of the treatment effect.

## Results

```{r}
#| label: analysis
#| echo: false

# Analysis results already loaded from output/analysis_results.rds
```

### Descriptive Statistics

The treatment group showed consistently higher measurements compared to controls:

```{r}
#| label: table-summary
#| echo: false

results$summary %>%
  knitr::kable(digits = 2, format = "simple",
               caption = "Summary statistics by group")
```

Mean values were `r round(results$summary %>% filter(group == "Control") %>% pull(mean), 2)`
for the control group and `r round(results$summary %>% filter(group == "Treatment") %>% pull(mean), 2)`
for the treatment group, representing a difference of
`r round(results$summary %>% filter(group == "Treatment") %>% pull(mean) - results$summary %>% filter(group == "Control") %>% pull(mean), 2)` units.

### Statistical Tests

The t-test comparing groups revealed a significant difference
(*t* = `r round(results$t_test$statistic, 3)`,
*p* = `r round(results$t_test$p.value, 4)`).
The linear regression model confirmed this finding, with the treatment effect coefficient
of `r round(coef(results$lm)[2], 3)` units.

### Visualizations

```{r}
#| label: figures
#| echo: false

knitr::include_graphics(c("figures/boxplot.pdf", "figures/timeseries.pdf"))
```

**Figure 1** displays the distribution of measurements by group, illustrating the separation
between control and treatment responses. Individual points are overlaid on the boxplots to show
data density. **Figure 2** shows how mean values changed over the measurement dates, with
both groups maintaining consistent differences across time points.

## Discussion

Our analysis provides strong evidence that the treatment significantly increases measured values
compared to controls. The effect is both statistically significant and practically meaningful,
with treatment values approximately 5 units higher than controls on average.

The consistency of this effect across two measurement dates suggests a robust treatment response
rather than a transient effect. These findings align with the theoretical expectation that the
treatment would produce elevated measurements and support the efficacy of the intervention.

Future work should investigate the mechanism underlying this treatment effect and explore dose-response
relationships to optimize the intervention.

## Conclusion

This study demonstrates a clear and statistically significant difference between control and treatment
groups, with the treatment producing elevated measurements. The results provide evidence supporting the
effectiveness of the experimental intervention.

## References
